Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-15 ms.tex
more

@@

\begin{figure*}
\begin{center}
\epsfig{file=results.eps, width=7.0in}
\caption{Our best-fit $T_2$, binned to 27.5$'$ resolution}
\end{center}
\end{figure*}

@@

>>>>

For each pixel, we initialize the Markov chain to have $T_2$ = $\bar{T}_2$ and
. We run 500 steps of burn-in and then 2000 steps during which we keep track
of the proposed $T_{2, j}$ and $I_{545, j}$ values. We use these 2000 values 
for each parameter to compute estimates of each parameter,  $T_2$ = 
$\langle T_{2, j} \rangle$, $I_{545}$ = $\langle I_{545, j} \rangle$, and of 
each parameter's variance, $\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$ and $\sigma^2_{I_{545}}$=$\langle I^2_{545, j} 
\rangle-\langle I_{545, j} \rangle ^2$

@@

\begin{figure}
\begin{center}
\epsfig{file=tcomparison.eps, width=3.3in}
\caption{Comparison of SFD temperature, two-component model $T_2$, and 
\cite{planckdust} temperature. Note the differing colorscales. Both models 
incorporating \PLANCK~data clearly show a major improvement in resolution 
relative to SFD.}
\end{center}
\end{figure}

@@

\begin{figure*} [ht]
\begin{center}
\epsfig{file=results.eps, width=7.0in}
\caption{Our best-fit $T_2$, binned to 27.5$'$ resolution}
\end{center}
\end{figure*}
